Single-step Hybrid Predition

### 2016-11-22 reports/agronomic_data.Rmd
Move predictor_subsetting.R content into reports file

## Correlation
```{r Agro-Correlation, echo = FALSE, fig.cap = "Pairwise correlations among seven agronomic traits for the full set of hybrids and the reduced set of hybrids, respectively."}
par(mar = c(0, 1, 0, 0),
    mfrow = c(1, 2))
all_pheno %>%
  select(-Reduced_Data) %>%
  spread(key = Trait, value = Observed) %>%
  as.data.frame() %>%
  remove_rownames() %>%
  column_to_rownames(var = "G") %>%
  cor() %>%
  corrplot::corrplot(col = viridis(256),
                     method = "color",
                     diag = FALSE,
                     cl.pos = "b",
                     tl.pos = "d",
                     tl.srt = 60,
                     order = "hclust",
                     addCoef.col = "black",
                     title = "Full",
                     mar = c(0, 1, 1, 0))
reduced_pheno %>%
  filter(Reduced_Data == "yes") %>%
  select(-Reduced_Data) %>%
  spread(key = Trait, value = Observed) %>%
  as.data.frame() %>%
  remove_rownames() %>%
  column_to_rownames(var = "G") %>%
  cor() %>%
  corrplot::corrplot(col = viridis(256),
                     method = "color",
                     diag = FALSE,
                     cl.pos = "b",
                     tl.pos = "d",
                     tl.srt = 60,
                     order = "hclust",
                     addCoef.col = "black",
                     title = "Reduced",
                     mar = c(0, 1, 1, 0))
```

>>>>

## Correlation
```{r Agro-Correlation, echo = FALSE, fig.cap = "Pairwise correlations among seven agronomic traits for the full set of hybrids (upper diagonal) and the reduced set of hybrids (lower diagonal), respectively."}
cor_coeffs <- all_pheno %>%
  rbind(., reduced_pheno) %>%
  spread(key = Trait, value = Observed) %>%
  split(.$Reduced_Data) %>%
  map(~select(., -Reduced_Data)) %>%
  map(as.data.frame) %>%
  map(remove_rownames) %>%
  map(column_to_rownames, var = "G") %>%
  map(cor) %>%
  map_at(.at = "no", .f = ~.[upper.tri(., diag = FALSE)]) %>%
  map_at(.at = "yes", .f = ~.[lower.tri(., diag = FALSE)])
traits <- levels(all_pheno$Trait)
cor_mat <- diag(nrow = 7, ncol = 7)
cor_mat[upper.tri(cor_mat, diag = FALSE)] <- cor_coeffs$no
cor_mat[lower.tri(cor_mat, diag = FALSE)] <- cor_coeffs$yes
dimnames(cor_mat) <- list(traits, traits)
cor_mat %>%
  corrplot::corrplot(col = viridis(256),
                     method = "color",
                     diag = FALSE,
                     cl.pos = "b",
                     tl.pos = "d",
                     tl.srt = 60,
                     order = "hclust",
                     addCoef.col = "black",
                     mar = c(0, 1, 1, 0))
```

### 2016-11-22 reports/loocv_reduced.Rmd
Move predictor_subsetting.R content into reports file

Compute the average standard deviation for each combination of predictors and 
traits -> http://stats.stackexchange.com/a/26647
```{r Coefficient-of-Variation, cache = TRUE}
coefficient_of_variation <- function(x, y) {
  sqrt(mean(x)) / mean(y)
}
cv_df <- pred_df %>%
  split(list(.$Trait, .$Predictor)) %>%
  map(~coefficient_of_variation(x = .$var_yhat, y = .$yhat)) %>%
  stack() %>%
  separate(col = ind, into = c("Trait", "Predictor"), sep = "[.]") %>%
  rename(CV = values) %>%
  tbl_dt() %>%
  mutate(Predictor = as.factor(Predictor),
         Trait = as.factor(Trait))
```

Combine predictive abilities and coefficients of variation for all predictor
and trait combinations for plotting.
```{r Organize-Data, cache = TRUE}
overview_df <- pred_df %>%
  group_by(Predictor, Trait) %>%
  summarize(r = cor(y, yhat)) %>%
  ungroup() %>%
  as.data.frame() %>%
  left_join(y = cv_df, by = c("Predictor", "Trait")) %>%
  as_tibble() %>%
  mutate(Predictor = as.factor(Predictor),
         Predictor = forcats::fct_reorder(Predictor, CV),
         Trait = fct_relevel(Trait,
                             "DMY", "DMC", "ADF", "FAT", "PRO",
                             "STA", "SUG"),
         Group = ifelse(Predictor %in% c("snp42-none-none",
                                         "ped42-none-none",
                                         "mrna42-none-none"),
                        yes = "Reduced", no = "Full")
  ) %>%
  mutate(Group = as.factor(Group))

# Specify a unified predictor order.
pred_order <- c("ped42-none-none", "snp42-none-none", "mrna42-none-none",
                "ped100-none-none", "snp100-none-none", "ped100-snp77-none",
                "ped100-mrna42-none", "snp100-mrna42-none",
                "ped100-snp77-mrna42")
```

Distribution of predicted and observed values.
Bear in mind that the distribution of the observed values will be different
for different predictors because some predictors "xx42" and "xx77", where
'xx' denotes a predictor, contain less hybrids than there are available 
(i.e. "xx100").
```{r Distribution-y-yhat, cache = TRUE, fig.height = 12, fig.cap = "Frequency polygon of observed and predicted values for seven agronomic traits (columns) and nine sets of predictors (rows)."}
legend_labs <- expression(y, hat(y))
pred_df %>%
  filter(Predictor != "snp77-none-none") %>%
  gather(key = Value, value = `Phenotypic Value`, y, yhat) %>%
  mutate(Predictor = fct_relevel(Predictor, pred_order)) %>%
  ggplot(aes(x = `Phenotypic Value`, color = Value)) +
  geom_freqpoly() +
  scale_color_manual(values = c("#1f78b4", "#e31a1c"), labels = legend_labs) +
  facet_grid(Predictor ~ Trait, scales = "free") +
  theme_bw() +
  theme(legend.position = "top",
        strip.text.y = element_text(size = 7)) +
  guides(color = guide_legend(override.aes = list(size = 2))) +
  ylab("Frequency")
```

Compare the coefficients of variation for all predictor-trait combinations.
```{r Coefficient-of-Variation-Plot, cache = TRUE, fig.cap = "Coefficient of variation for seven agronomic traits and nine sets of predictors."}
overview_df %>%
  filter(Predictor != "snp77-none-none") %>%
  mutate(Predictor = fct_relevel(Predictor, pred_order)) %>%
  ggplot(aes(x = CV, y = Predictor)) +
  geom_segment(aes(yend = Predictor), xend = 0, color = "gray50") +
  geom_point(aes(color = Predictor), size = 3) +
  scale_color_viridis(discrete = TRUE, option = "inferno") +
  facet_wrap(~ Trait, scales = "free_x") +
  theme_bw() +
  theme(panel.grid.major.y = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = c(0.7, 0.13)
  ) +
  guides(color = guide_legend(ncol = 2,
                              reverse = FALSE)) +
  xlab("Coefficient of Variation") +
  ylab("Predictor Set") +
  xlim(0, NA)
```

>>>>

## Distribution of predicted and observed values
```{r Distribution-y-yhat, cache = TRUE, fig.height = 12, fig.cap = "Frequency polygon of observed and predicted values for seven agronomic traits (columns) and nine sets of predictors (rows)."}
# Specify a unified predictor order.
pred_order <- c("ped42-none-none", "snp42-none-none", "mrna42-none-none",
                "ped100-none-none", "snp100-none-none", "ped100-snp77-none",
                "ped100-mrna42-none", "snp100-mrna42-none",
                "ped100-snp77-mrna42")
legend_labs <- expression(y, hat(y))
pred_df %>%
  filter(Predictor != "snp77-none-none") %>%
  gather(key = Value, value = `Phenotypic Value`, y, yhat) %>%
  mutate(Predictor = fct_relevel(Predictor, pred_order)) %>%
  ggplot(aes(x = `Phenotypic Value`, color = Value)) +
  geom_freqpoly() +
  scale_color_manual(values = c("#1f78b4", "#e31a1c"), labels = legend_labs) +
  facet_grid(Predictor ~ Trait, scales = "free") +
  theme_bw() +
  theme(legend.position = "top",
        strip.text.y = element_text(size = 7)) +
  guides(color = guide_legend(override.aes = list(size = 2))) +
  ylab("Frequency")
```

## Coefficient of variation for predicted values
We are interested in the variation in the predicted values relative to the 
arithmetic mean of the predicted values, separately for each agronomic trait and
each set of predictors:

$$
\begin{equation}
  \label{eq:CV}
CV = \sqrt{\frac{\sum_{i = 1}^{N} \sigma^{2}_{\hat{y}(i)} / N}{\sum_{i=1}^{N}\hat{y}_{i} / N}},
\end{equation}
$$

where $N$ denotes the number of hybrids.

```{r Coefficient-of-Variation, cache = TRUE}
coefficient_of_variation <- function(x, y) {
  sqrt(mean(x)) / mean(y)
}
cv_df <- pred_df %>%
  split(list(.$Trait, .$Predictor)) %>%
  map(~coefficient_of_variation(x = .$var_yhat, y = .$yhat)) %>%
  stack() %>%
  separate(col = ind, into = c("Trait", "Predictor"), sep = "[.]") %>%
  rename(CV = values) %>%
  tbl_dt() %>%
  mutate(Predictor = as.factor(Predictor),
         Trait = as.factor(Trait))

overview_df <- pred_df %>%
  group_by(Predictor, Trait) %>%
  summarize(r = cor(y, yhat)) %>%
  ungroup() %>%
  as.data.frame() %>%
  left_join(y = cv_df, by = c("Predictor", "Trait")) %>%
  as_tibble() %>%
  mutate(Predictor = as.factor(Predictor),
         Predictor = forcats::fct_reorder(Predictor, CV),
         Trait = fct_relevel(Trait,
                             "DMY", "DMC", "ADF", "FAT", "PRO",
                             "STA", "SUG"),
         Group = ifelse(Predictor %in% c("snp42-none-none",
                                         "ped42-none-none",
                                         "mrna42-none-none"),
                        yes = "Reduced", no = "Full")
  ) %>%
  mutate(Group = as.factor(Group))
```

## Predictive Abilities
```{r Coefficient-of-Variation-Plot, cache = TRUE, fig.cap = "Coefficient of variation for seven agronomic traits and nine sets of predictors."}
overview_df %>%
  filter(Predictor != "snp77-none-none") %>%
  mutate(Predictor = fct_relevel(Predictor, pred_order)) %>%
  ggplot(aes(x = CV, y = Predictor)) +
  geom_segment(aes(yend = Predictor), xend = 0, color = "gray50") +
  geom_point(aes(color = Predictor), size = 3) +
  scale_color_viridis(discrete = TRUE, option = "inferno") +
  facet_wrap(~ Trait, scales = "free_x") +
  theme_bw() +
  theme(panel.grid.major.y = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = c(0.7, 0.13)
  ) +
  guides(color = guide_legend(ncol = 2,
                              reverse = FALSE)) +
  xlab("Coefficient of Variation") +
  ylab("Predictor Set") +
  xlim(0, NA)
```
